---
title: "linreg"
author: "Brahmantio, B. B. & van Doorn, J."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
  knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```
  
```{r setup}
  library(ggplot2)
  library(gridExtra)
  library(grid)
  library(lab4group8)
```

# Using the linreg package
## Introduction
This package provides a Linear Regression Model as a function that returns the model as an Object. 

## Running the model
To run the model you need to input a *formula* and a *dataset*. This example uses the dataset *iris*, which is standard include in R. 

```{r iris, echo=FALSE}
  data(iris)
```

The model is of the form y~x, where y is the Sepal length depending on the x, the petal length.

```{r}
  linreg1 <- linreg(Sepal.Length~Petal.Length, data = iris)
```

In the command above we create an object of the class *linreg* which contains all the information that we need.

## Methods
The linreg object can be manipulated by using six different methods:

* print()
* plot() 
* resid() 
* pred() 
* coef()
* summary()

### print()
*linreg1$print()* prints the coefficients.

```{r}
  linreg1$print()
```

### plot()
*linreg1$plot()* plots two graphs. The first plots the Residuals vs the Fitted values. The second is a Scale-Locationo plot.

```{r, eval=FALSE}
  linreg1$plot()
```

### resid()
*linreg1$resid()* returns a vector with the residuals.

```{r}
  head(linreg1$resid())
```

### pred()
*linreg1$pred()* returns a vector with the predicted values.

```{r}
  head(linreg1$pred())
```

### coef()
*linreg1$coef()* returns the intercept plus the coefficients.

```{r}
  linreg1$coef()
```
### summary()
*linreg1$summary()* prints the coefficients with their standard error, t-values, and p-value, plus the estimate of standard deviation of the variance and the degrees of freedom.

```{r}
  linreg1$summary()
```
